---
title: "Taylor Data Pre-Registration"
format: html
editor: visual
---

```{r}
library(taylor)
library(dplyr)
taylor_album_songs <- taylor_album_songs
```

I am creating a pre-registration for a study with the hypothesis that tracks from Taylor's albums which have high danceability, energy, and tempo are more likely to be released as singles.

In order to complete this analysis, I will create a combined score 'pop', which is an established method of determining the degree to which a song is high energy in my vast reading of the literature (insert citation here). This takes the mean score of danceability, energy, and tempo, and combines them into a pop total score.

After creating this pop total score, I will evaluate a logistic regression model to examine the association between pop-ness of a song and likelihood of release as a single. I will control for whether or not it was a bonus track since bonus tracks are less likely to be released as singles.

```{r}
taylor_singles <- taylor_album_songs |> 
  mutate(std_tempo = scale(tempo)) |>
  mutate(std_dance = scale(danceability)) |> 
  mutate(std_energy = scale(energy)) |> 
  mutate(pop =  (std_tempo+std_dance+std_energy)/3) |> 
  select(track_name, bonus_track, pop,single_release) |> 
  mutate(single = if_else(is.na(single_release) == TRUE, 0, 1))
```

```{r}
release_model <- stats::glm(single~ pop+ bonus_track, data = taylor_singles, family = 'binomial')
summary(release_model)
```

```{r}

```

$Ln(single/1-single) = {\beta}_0+ {\beta}_1Pop + {\beta}_2Bonus$

\$\$

\$\$
