---
title: "Week 2 - Lecture 2: Intro to the Class Data"
format: html
editor: visual
---

```{r}
library(dplyr)
library(ggplot2)
```

1.  Read in Spotify Data

    ```{r}
    spotify_songs <- tidytuesdayR::tt_load('2020-01-21')$spotify_
    ```

2.  List all the variables in the dataset

    ```{r}
    names(spotify_songs)
    ```

3.  Identify how many artists there are in the database and place this in a sentence.

    ```{r}
    artist_n <- dplyr::n_distinct(spotify_songs$track_artist)
    ```

There are `r artist_n` artists in the database.

4.  List the subgenres of 'edm'

```{r}
edm <- spotify_songs %>% 
  filter(playlist_genre == 'edm') 
unique(edm$playlist_subgenre)
```

5.  Create a bar chart showing the average popularity of songs in the dataset across subgenres of edm

    ```{r}
    ggplot(edm, aes(fill = playlist_subgenre, y = track_popularity, x = playlist_subgenre)) + 
      geom_bar(stat = 'identity')
    ```

6.  In our in-class projects, we will create new variables to explore in the dataset (and add to the existing data dictionary in the tidy tuesday readme). Discuss with partner(s) 1-2 ideas for a new variable to add by manipulating the existing variables, and create these new variables in your version of the data. Discuss potential ideas for analysis which uses these new variables.
